%------------------------
% Author: Sheetal Patidar.
%------------------------

\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor} % Add the xcolor package for color support

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\color{blue}\scshape\raggedright\large % Change the color of the heading to blue
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}] % Change the color of the rule to black

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
  {\LARGE \textbf{Sheetal Patidar}} & \href{mailto:sheetalpatidar41@gmail.com}{sheetalpatidar41@gmail.com}\\
  \href{https://sheetalpatidar.github.io/portfolio/}{Portfolio: profile.com} & +91-750-980-3282 \\
  \href{https://github.com/SheetalPatidar}{Github: github.com/Sheetal} & CodeChef: \href{https://www.codechef.com/users/sheetal_0405}{User/sheetal0405} \\
\end{tabular*}

\vspace{8pt} % Add some vertical space between the contact info and the content

%-----------About Me-----------------
\vspace{3pt}

B.Tech Data Science student at IPS Academy with 1 year of web development expertise. I am passionate about leveraging my skills in creating efficient and innovative solutions. Energetic and dedicated, I strive to deliver high-quality results and make a significant impact. I am ready to contribute to a dynamic team and take on new challenges.

\vspace{8pt} % Add some vertical space after the "About Me" section




%-----------EDUCATION-----------------
\section{\color{blue}Education} % Change the heading color to dark black
\resumeItemListStart
\resumeItem{\textbf{Institute of Engineering and Science IPS Academy, Indore, India }\hfill July 2020 - June 2024\\
Bachelor of Technology - Computer Science and Engineering\\
CGPA: 8.65\\
\vspace{4pt}} % Adjust the space as per your preference

\resumeItem{\textbf{Scholar’s Yard School Indore, India}\\
Higher secondary education - Class XII - Maths\\
Percentage: 75\\
\vspace{4pt}} % Adjust the space as per your preference

\resumeItem{\textbf{Maharshi Vidhya Mandir Khargone, India}\\
Secondary School - Class X\\
Percentage: 95}
\resumeItemListEnd


%-----------SKILLS-----------------
\section{\color{blue}Skills Summary} % Change the heading color to dark black
\resumeItemListStart
\resumeItem{\textbf{Languages}: Python, PHP, C++, JavaScript (React), SQL, HTML, CSS}
\vspace{-3pt}

\resumeItem{\textbf{Frameworks}: Scikit, Numpy, Pandas, OpenCV, Django, TensorFlow, CodeIgniter, NodeJS}
\vspace{-3pt}

\resumeItem{\textbf{Tools}: Postman, Jupyter, UNIX, Docker, GIT, PostgreSQL, MySQL, SQLite, MongoDB, Data Visualization Software: Excel, \tab PowerBI, Tableau}
\vspace{-3pt}

\resumeItem{\textbf{Skills}: Data Visualization, Statistics and probability, Problem Solving, Machine Learning, Data Analytical Skills, Web Development}
\vspace{-3pt}

\resumeItem{\textbf{Soft Skills}: Leadership, Event Management, Writing, Public Speaking, Time Management}
\vspace{-3pt}

\resumeItemListEnd


%-----------EXPERIENCE-----------------
\section{\color{blue}Experience} % Change the heading color to blue
\resumeItemListStart
\resumeItem{\textbf{IPS Academy (CMS)} \hfill July 2022 - July 2023\\
Full Stack Developer (Full-time)\\
\vspace{-5pt}

\begin{itemize}
    \item Worked as an intern in the web development team at IPS Academy, where I gained practical experience in developing CMS using CodeIgniter and MERN Stack API.
\vspace{-3pt}
    
    \item Involved in both front-end and back-end development tasks, including UI design, database management, and API integration.
\vspace{-3pt}
    
    \item Contributed to the development of the college website, handling tasks such as website maintenance, bug fixing, and content management.
\vspace{-3pt}
    
\end{itemize}}
\resumeItemListEnd

%-----------PROJECTS-----------------
\section{\color{blue}Projects} % Change the heading color to blue
\resumeItemListStart
\resumeItem{\textbf{DataBliss}
\vspace{-7pt}

\begin{itemize}

    \item Collaboratively developed a billing software for businesses as a side project.
\vspace{-3pt}
    
    \item Utilized CodeIgniter 4 framework to implement a robust and scalable MVC architecture.
\vspace{-3pt}
    
    \item Implemented jQuery for interactive and dynamic user interfaces, improving user experience.
\end{itemize}}
\resumeItem{\textbf{Expense Management}
\vspace{-7pt}

\begin{itemize}
    \item Developed using React (JavaScript library for building user interfaces).
    \item Implemented user-friendly interface for adding, editing, and categorizing expenses.
\end{itemize}}
\resumeItemListEnd

%-----------HONORS AND AWARDS-----------------
\section{\color{blue}Honors and Awards} % Change the heading color to blue
\resumeItemListStart
\resumeItem{\textbf{Participated in 36 Hours Hackathon (Kriyeta) at Acropolis Institute of Technology and Research (06/2023)}\\
Demonstrated strong problem-solving, critical thinking, and teamwork skills throughout the event. Collaborated with a diverse team to develop an innovative solution, demonstrating adaptability and resilience in a fast-paced environment.}
\vspace{-3pt}


\resumeItem{\textbf{Runner-up in District Chess Nodal’s Competition (11/2022)}\\
Demonstrated exceptional strategic thinking, concentration, and skill in navigating intense chess matches.}
\vspace{-3pt}

\resumeItem{\textbf{Udhymita}\\
For participating in Pitch-Up 2021 – idea pitching competition organized by entrepreneurship development cell (EDC), SHRI Vaishnav Vidyapeeth Vishwavidyalaya, Indore.}
\vspace{-3pt}

\resumeItem{\textbf{Acropolish}\\
For actively participating in INDINNOVATE – Ideas Accelerated, virtual National idea contest.}
\vspace{-3pt}

\resumeItemListEnd

%-----------VOLUNTEER EXPERIENCE-----------------
\section{\color{blue}Volunteer Experience} % Change the heading color to blue
\resumeItemListStart
\resumeItem{\textbf{Google Student Developer Club}\\
As the Event Management Lead at GDSC, I planned, executed and managed various events, collaborated with team members.}

\resumeItem{\textbf{Student Coordinator}\\
I was Student Coordinator for an event at IPS Academy where I managed the anchoring part with my other team members.}
\resumeItemListEnd

\end{document}